\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-08-14 paper/manuscript.tex
topic coherence, by number of topics, plotted
added map of indiana with mayoral partisanship
minor changes to map
updated the tex file and delete/moved some other stuff

\begin{figure}[!ht]
	\centering
	%\caption{Population coverage}
	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
\end{figure}

@@

>>>>

\begin{figure}[!ht]
	\centering
	\caption{Percentage of state population covered.}
	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
\end{figure}

@@

%Number of topics vs. tophic coherence
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Topic coherence, varying the number of topics. The red line represents the mean topic coherence for each number of topics.}
	\label{numtopics_coherence}
	\includegraphics[width=\linewidth]{figures/coherence_numberoftopics.pdf}
\end{figure}

%Indiana map
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Cities in the corpus, by partisanship of mayor.}
	\label{indiana_map}
	\includegraphics[height=0.75\textheight]{figures/indiana_map.pdf}
\end{figure}

%partisan topics
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{The most partisan topics. The number in parenthesis indicates how many times more the topic appears on average (measured through the number of words of the topic throughout the documents) in the respective party's corpus (indicated by the color).}
	\label{partisan_topics}
	\includegraphics[height=0.75\textheight]{figures/partisanTopics.pdf}
\end{figure}
